\documentclass{article}

\begin{document}
\title{Preparing Bacteria for Flow Cytometry. Protocol taken from Magdalena
 in Joe Kaguni's lab.}
\maketitle

\textbf{Reference:} Steen, H.B., Skarstad K., Boye E. (1968) Flow Cytometry of
bacteria: cell cycle kinetics and effects of antibiotics. Ann NY Acad Sci 468:
329-338.
\newline\newline
\begin{itemize}
\item{Pellet the cells by centrifugation, and discard supernatant.}
\item{Resuspend the pellet in an equal volume of Steen Buffer
(10mM Tris-HCl pH 7.8 \textbf{(Magdalena used pH 7.4)},
10mM MgSO$_{4}$)}
\item{Spin as above, discard supernatant.}
\item{Resuspend the pellet in a small volume of Steen Buffer (concentrate 
bacteria about 10 times).}
\item{Pass bacteria through a 22-gauge needle into $77\%$ ice cold ethanol to 
dilute bacteria 10 times (e.g. 0.5ml to 4.5ml of ethanol). Final concentration
of ethanol $70\%$, desired OD of bacteria 0.2 or more.}
\item{Bacteria can be stored in ethanol for weeks.}
\item{Prepare DAPI solution in Steen Buffer (1-2$\mu$g/ml).}
\item{Remove 1.5ml bacteria from ethanol, pellet by centrifugation.}
\item{Wash pellet in Steen Buffer, centrifuge.}
\item{Resuspend pellet in 0.5ml of DAPI solution. Louis needs about $2*10^{6}$
cells in 0.5ml stain for at least 2 hours on ice, or overnight in a 
refrigerator.}
\end{itemize}
Note: other protocols use 10mM Tris-HCl pH 7.5, 10mM MgCl$_{2}$ instead of
Steen Buffer, and filter through 0.22$\mu$m filter.
\newline\newline
\textbf{Also see:} Akerlund, T., Nordstrom, K., Bernander R. (1995) Analysis
of Cell Size and DNA Content in Exponentially Growing and Stationary-Phase
Batch Cultures of \textit{Escherichia coli}. Journal of Bacteriology, Dec.
1995, Vol 177, No. 23, p.6791-6797.
\end{document}
